A thesis draft

### 2018-11-15 res/sections/25-Tests.tex
Add listing, change some settings

The previous test make us see how much Docker is faster than a traditional
virtual machine. The test, though, was performed on a single node, interacting
directly with Docker and not through the orchestrator we used in the thesis
development, in other words Kubernetes. The following measurement will allow us
to see the time required in order to deploy an SFC of different elements in a
Kubernetes environment. The deployment consisted in a Pod inside a Deployment
definition with a Service related, to simulate a real VNF. After the Pod
startup, a request is made to a backend designed to count the chain elements
that have successfully boot-up that will return, eventually, the timing when all
the VNFs are up and running.

% Add SFC definition, graphs, talk about them

>>>>

The previous test make us see how much Docker is faster than a traditional
virtual machine. The test, though, was performed on a single node, interacting
directly with Docker and not through the orchestrator we used in the thesis
development, in other words Kubernetes. The following measurement will allow us
to see the time required in order to deploy an SFC of different elements in a
Kubernetes environment. The deployment consist in a Pod inside a Deployment
definition with a related Service, to simulate a real VNF. After the Pod
startup, a request is made to a backend designed to count the chain elements
that have successfully boot-up returning, eventually, the overall start up 
timing.

% TODO: missing YAML definition: [language=YAML]
%https://tex.stackexchange.com/questions/152829/how-can-i-highlight-yaml-code-in
%- a-pretty-way-with-listings
\lstinputlisting{res/code/sfc_test.yaml}

As is possible to see from the YAML definition, the test % talk about 
%imagepull policy
% Add SFC definition, graphs, talk about them
